### 2023-03-13 output/crime_140m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & twenty_seventeen_any_crime_140m & 0.93 & -0.01 & 0.91 & 0.00 & 0.99 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,396.49 & 0.00 \\
 & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,321.13 & 0.20 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 178.07 & 0.03 \\
 & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & For cause & 0.17 & -0.01 & 0.48 & -0.03 & 0.35 \\
 & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & twenty_seventeen_group_1_crimes_200m & 1.38 & 0.09 & 0.35 & 0.02 & 0.89 \\
\cline{1-7}
\multirow[c]{7}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.01 & 0.24 & 0.05 & 0.01 \\
 & job_density_2013 & 16,069.14 & 3,197.93 & 0.16 & 5,413.87 & 0.16 \\
 & poor_share2010 & 0.27 & 0.01 & 0.14 & -0.01 & 0.33 \\
 & popdensity2010 & 23,086.04 & 1,373.15 & 0.06 & 483.47 & 0.68 \\
 & rent_twobed2015 & 1,339.99 & -29.55 & 0.50 & 30.88 & 0.67 \\
 & share_white2010 & 0.31 & 0.02 & 0.10 & 0.05 & 0.04 \\
 & traveltime15_2010 & 0.16 & 0.01 & 0.23 & 0.01 & 0.20 \\
\cline{1-7}
\textit{Panel C} & no_cause & 0.05 & -0.05 & 0.00 & -0.08 & 0.00 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & 0.07 & 0.00 & 0.11 & 0.00 \\
 & isEntityD & 0.01 & -0.04 & 0.00 & 0.01 & 0.17 \\
 & isEntityP & 0.81 & 0.10 & 0.00 & 0.12 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-13 output/crime_140m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 140m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_140m & 0.00 & 0.91 \\
 & pre_treatment_change_in_any_crime_140m & 0.14 & 0.45 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.00 & 0.19 \\
 & Share below poverty line & 0.00 & 0.14 \\
 & Population density (2010) & 0.07 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.00 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.04 & 0.48 \\
 & No cause & 0.49 & 0.00 \\
 & Non-payment of rent & 0.02 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.92 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.30 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Assault-Related Crime Incidents Within 200m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_200m & 0.00 & 0.35 \\
 & pre_treatment_change_in_group_1_crimes_200m & 0.90 & 0.96 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.24 \\
 & job_density_2013 & 0.00 & 0.16 \\
 & med_hhinc2016 & 0.59 & 0.19 \\
 & poor_share2010 & 0.00 & 0.14 \\
 & popdensity2010 & 0.00 & 0.06 \\
 & rent_twobed2015 & 0.00 & 0.50 \\
 & share_white2010 & 0.00 & 0.10 \\
 & traveltime15_2010 & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.92 & 0.48 \\
 & no_cause & 0.00 & 0.00 \\
 & non_payment & 0.06 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.81 & 0.00 \\
 & hasAttyP & 0.02 & 0.00 \\
 & isEntityD & 0.00 & 0.00 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-13 output/crime_200m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_200m & 18.26 & 0.79 & 0.36 & 0.62 & 0.71 \\
 & pre_treatment_change_in_any_crime_200m & -2.30 & 0.26 & 0.62 & 0.75 & 0.43 \\
\cline{1-7}
\multirow[c]{6}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,395.48 & 0.00 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 531.25 & 0.71 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 176.95 & 0.03 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel C}} & No cause & 0.05 & -0.05 & 0.00 & -0.11 & 0.00 \\
 & Non-payment of rent & 0.78 & 0.07 & 0.00 & 0.16 & 0.00 \\
\cline{1-7}
\textit{Panel D} & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & twenty_seventeen_group_0_crimes_50m & 1.43 & -0.20 & 0.16 & -0.16 & 0.26 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & job_density_2013 & 16,069.14 & 3,197.93 & 0.16 & 843.09 & 0.71 \\
 & popdensity2010 & 23,086.04 & 1,373.15 & 0.06 & -365.58 & 0.58 \\
 & traveltime15_2010 & 0.16 & 0.01 & 0.23 & -0.00 & 0.34 \\
\cline{1-7}
\textit{Panel C} & non_payment & 0.78 & 0.07 & 0.00 & -0.00 & 0.92 \\
\cline{1-7}
\textit{Panel D} & isEntityP & 0.81 & 0.10 & 0.00 & 0.01 & 0.40 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-13 output/crime_200m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 200m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_200m & 0.00 & 0.72 \\
 & pre_treatment_change_in_any_crime_200m & 0.00 & 0.07 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.00 & 0.19 \\
 & Share below poverty line & 0.00 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.13 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.94 & 0.48 \\
 & No cause & 0.00 & 0.00 \\
 & Non-payment of rent & 0.08 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.80 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.05 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Crime Incidents Within 50m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_0_crimes_50m & 0.00 & 0.16 \\
 & pre_treatment_change_in_group_0_crimes_50m & 0.22 & 0.06 \\
\cline{1-4}
\multirow[c]{7}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.09 & 0.24 \\
 & job_density_2013 & 0.00 & 0.16 \\
 & med_hhinc2016 & 0.73 & 0.19 \\
 & poor_share2010 & 0.50 & 0.14 \\
 & popdensity2010 & 0.04 & 0.06 \\
 & share_white2010 & 0.96 & 0.10 \\
 & traveltime15_2010 & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.13 & 0.48 \\
 & no_cause & 0.24 & 0.00 \\
 & non_payment & 0.03 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.34 & 0.00 \\
 & hasAttyP & 0.09 & 0.00 \\
 & isEntityD & 0.38 & 0.00 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-03-13 output/crime_90m/tables/balance_table.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & twenty_seventeen_any_crime_90m & 0.68 & 0.02 & 0.77 & -0.12 & 0.26 \\
 & pre_treatment_change_in_any_crime_90m & -0.02 & 0.01 & 0.91 & 0.03 & 0.76 \\
\cline{1-7}
\multirow[c]{8}{3cm}{\textit{Panel B}} & Share with bachelor's degree & 0.32 & 0.01 & 0.24 & 0.07 & 0.00 \\
 & Jobs per square mile (2010) & 16,069.14 & 3,197.93 & 0.16 & 12,393.10 & 0.00 \\
 & Median household income (2016) & 48,035.65 & 1,777.65 & 0.19 & 3,315.55 & 0.20 \\
 & Share below poverty line & 0.27 & 0.01 & 0.14 & 0.00 & 0.85 \\
 & Population density (2010) & 23,086.04 & 1,373.15 & 0.06 & 537.03 & 0.70 \\
 & Median two bedroom rent (2015) & 1,339.99 & -29.55 & 0.50 & 177.10 & 0.03 \\
 & Share white (2010) & 0.31 & 0.02 & 0.10 & 0.09 & 0.00 \\
 & Share with commute $<$15 minutes (2010) & 0.16 & 0.01 & 0.23 & 0.02 & 0.02 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & Plaintiff has an attorney & 0.88 & 0.07 & 0.00 & 0.21 & 0.00 \\
 & Plaintiff is an entity & 0.81 & 0.10 & 0.00 & 0.23 & 0.00 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & twenty_seventeen_group_1_crimes_150m & 0.86 & 0.14 & 0.05 & 0.03 & 0.68 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.32 & 0.01 & 0.24 & -0.01 & 0.60 \\
 & poor_share2010 & 0.27 & 0.01 & 0.14 & -0.01 & 0.43 \\
 & share_white2010 & 0.31 & 0.02 & 0.10 & -0.00 & 0.94 \\
 & traveltime15_2010 & 0.16 & 0.01 & 0.23 & -0.00 & 0.44 \\
\cline{1-7}
\textit{Panel C} & non_payment & 0.78 & 0.07 & 0.00 & 0.00 & 0.99 \\
\cline{1-7}
\textit{Panel D} & isEntityP & 0.81 & 0.10 & 0.00 & 0.01 & 0.38 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-03-13 output/crime_90m/tables/pre_treatment_covariate_tests.tex
updated analysis utilities to accomodate new outcomes

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Any Crime Incidents Within 90m, Dec. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_any_crime_90m & 0.00 & 0.77 \\
 & pre_treatment_change_in_any_crime_90m & 0.00 & 0.91 \\
\cline{1-4}
\multirow[c]{8}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Share with bachelor's degree & 0.00 & 0.24 \\
 & Jobs per square mile (2010) & 0.00 & 0.16 \\
 & Median household income (2016) & 0.00 & 0.19 \\
 & Share below poverty line & 0.04 & 0.14 \\
 & Population density (2010) & 0.00 & 0.06 \\
 & Median two bedroom rent (2015) & 0.00 & 0.50 \\
 & Share white (2010) & 0.00 & 0.10 \\
 & Share with commute $<$15 minutes (2010) & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.15 & 0.48 \\
 & No cause & 0.65 & 0.00 \\
 & Non-payment of rent & 0.07 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.32 & 0.00 \\
 & Plaintiff has an attorney & 0.00 & 0.00 \\
 & Defendant is an entity & 0.59 & 0.00 \\
 & Plaintiff is an entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Assault-Related Crime Incidents Within 150m, Oct. 2022 & Plaintiff Victory \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & twenty_seventeen_group_1_crimes_150m & 0.00 & 0.05 \\
 & pre_treatment_change_in_group_1_crimes_150m & 0.40 & 0.45 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.24 \\
 & med_hhinc2016 & 0.58 & 0.19 \\
 & poor_share2010 & 0.00 & 0.14 \\
 & share_white2010 & 0.00 & 0.10 \\
 & traveltime15_2010 & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.31 & 0.48 \\
 & no_cause & 0.08 & 0.00 \\
 & non_payment & 0.04 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.47 & 0.00 \\
 & hasAttyP & 0.07 & 0.00 \\
 & isEntityD & 0.80 & 0.00 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}
